Clicks and Cliques

### 2018-12-23 papersoul.Rnw

qplot(data=aux, x=dim2,y=QSB,fill=rmdg,geom='tile')+ theme(axis.text.x = element_text(angle=90, size=I(12)), axis.title.x=element_blank() )  +scale_fill_gradient(low="white", high="red") +theme(legend.position = 'none')
@
\caption{Illustration of the differences in important variables by community \label{imp.st}. For each variable, red intensity represent the variable relative importance, i.e. in which community that variable is more important than the average. White indicates variables below importance average.}
\end{figure}

>>>>

a <- aux %>% select(QSB,dim2, rmdg) %>% spread(dim2,rmdg) %>% 
  select(-QSB) %>% cor()

cl <- abs(1-a) %>%  as.dist() %>% hclust( method = 'ward.D')

ggplot(data = aux, aes(x = fct_relevel(dim2, cl$labels[cl$order]), y = QSB, fill = rmdg )) +
  geom_tile() +
  theme(axis.text.x = element_text(angle = 90, size = I(12)), axis.title.x = element_blank() )  + scale_fill_gradient(low = "white", high = "red") + theme(legend.position = 'none')

@
\caption{Illustration of the differences in important variables by community \label{imp.st}. For each variable, red intensity represent the variable relative importance, i.e. in which community that variable is more important than the average. White indicates variables below importance average.}
\end{figure}
